\bf Model Visualization Techniques for a Social Network Model

### 2018-10-03 paper-child.Rnw
change all plots to grayscale (minus ggpairs because it won't do it i guess?)

ggplot(data = simu2) +
  geom_density(aes(x = estimate, fill = Model), alpha = .5) +
  facet_wrap(~parameter, scales = 'free') +
  ThemeNoNet +
  theme(legend.position = 'bottom')
@

@@

<<sigtesting, fig.show = 'hold', out.width='\\textwidth', fig.height=2, fig.cap="Significant effects for the two data sets, at a significance level of 0.10 or lower as calculated by the Wald-type test available in the SIENA software.", error=FALSE>>=
smfr_effs <- read_csv("data/effects_significance_smallFriends.csv")
smfr_effs$inter1[is.na(smfr_effs$inter1)] <- "none"
library(ggrepel)
set.seed(12345678)
smfr_effs %>% filter(type == "eval" & Waldpval <=0.10) %>%
ggplot(aes(x = estimate, y = Waldpval, color = inter1)) +
  #geom_errorbarh(aes(xmin = estimate - se, xmax = estimate + se), color = 'black') +
  geom_vline(xintercept = 0) +
  geom_point(size = 3) +
  #geom_text_repel(aes(label = shortName)) +
  scale_color_brewer(palette = "Paired", name = "Interaction\nVariable") +
  ggtitle("Significant effects at level 0.10 for friendship data") +
  coord_flip() +
  ThemeNoNet
sen_effs <- read_csv("data/congress/senateModelSigEffects.csv")
#sen_effs$Waldpval <- parse_number(sen_effs$Waldpval)
sen_effs$inter1[is.na(sen_effs$inter1)] <- "none"
ggplot(data = sen_effs %>% filter(Waldpval <=0.10), aes(x = estimate, y = Waldpval, color = inter1)) +
  # geom_errorbarh(aes(xmin = estimate - se, xmax = estimate + se), color = 'black') +
  geom_vline(xintercept = 0) +
  geom_point(size = 3) +
  #geom_text_repel(aes(label = shortName)) +
  scale_color_brewer(palette = "Paired", name = "Interaction\nVariable") +
  ggtitle("Significant effects at level 0.10 for senate data") +
  coord_flip() +
  ThemeNoNet
@

@@

ggplot(data = combinedavgs) +
  geom_net(aes(from_id = from, to_id = to, linewidth= linewidth),
           directed = T, curvature = .2, labelon=T, size = 4,
           arrow = arrow(angle = 20, type = "open", length = unit(.2, "cm")), ecolour = "#969696", fiteach = T,
           color = "#252525", hjust = .5, vjust = .5, labelcolour = 'white', fontsize = 3, arrowgap = .02,
           singletons = T) +
  ThemeNet + theme(panel.background = element_rect(color = 'black')) +
  facet_wrap(~cat)
@

@@

%Outdegree and reciprocity have the same inverse relationship for both data sets. For the friendship data, the inclusion of $\\beta_3$ has strong effect on the estimates of the other two parameters, but not for the senate data.
<<compareModels, fig.cap="Density plots of objective function parameter estimates from repeatedly fitting models M1, M2, and M3 to the example data. ", fig.height = 3>>=
simu2$data <- "friends"
senateEsts$data <- "senate"
allDataEsts <- rbind(senateEsts, simu2)
allDataEsts$parameter <- as.factor(allDataEsts$parameter)
allDataEsts$parameter <- ordered(allDataEsts$parameter, levels = c(paste0("alpha", 1:3),paste0("beta", 1:4)))
ggplot(allDataEsts %>% filter(str_detect(parameter, "beta"))) +
  geom_density(aes(x = estimate, fill = Model), alpha = .5) +
  facet_grid(data~parameter, scales = "free", labeller = "label_both") +
  ThemeNoNet +
  theme(legend.position = 'bottom')
@

@@

simu2 <- read.csv("data/simulation-1000-M1-M2-M3.csv")
simu_spread <- simu2 %>% spread(parameter, estimate)
ggpairs(simu_spread, columns = 3:8, ggplot2::aes(colour=Model, alpha = .5)) + theme(plot.title = element_text(size = 10,
                                            face = 'plain', angle = 0, family = "Times New Roman"),
                  axis.title.x = element_text(size = 10,
                                            face = 'plain', angle = 0, family = "Times New Roman", inherit.blank = T),
                  axis.title.y = element_text(size = 10,
                                            face = 'plain', angle = 90, inherit.blank = T),
                  axis.text.x= element_text(size = 10,
                                            face = 'plain', angle = 90, inherit.blank = TRUE),
                 # axis.text.x.bottom = element_text(size = 10,
             #                               face = 'plain', angle = 90, inherit.blank = TRUE),
                  axis.text.y = element_text(size = 10,
                                            face = 'plain', angle = 0, family = "Times New Roman", inherit.blank = T),
                #  axis.text.y.right = element_text(size = 12,
               #                             face = 'plain', angle = 0, family = "Times New Roman", inherit.blank = T),
                  strip.text.x = element_text(size = 12,
                                            face = 'plain', angle = 0, family = "Times New Roman",
                                            margin = margin(t = 3, r = 0, b = 3, l = 0, unit = "pt"), inherit.blank = T),
                  strip.text.y =element_text(size = 12,
                                            face = 'plain', family = "Times New Roman", angle = 90,margin = margin(t = 3, r = 3, b = 3, l = 3, unit = "pt"),inherit.blank = T),
                  strip.background = element_rect(colour = "black", fill = "white")
                    )
@

@@

sfmsall5 <- sfmsall4 %>% ungroup %>% add_row(ms = max(sfmsall4$ms) + 1,
        eid = wave2$eid,
        count = NA,
        alpha = 1,
        from = wave2$from,
        to = wave2$to,
        total = wave2$total,
        plotorder = wave2$plotorder)
sfmsall5$alphaFctr <- cut(sfmsall5$alpha, c(0,.01, .05, .10, .25, .5, .75, 1, 1.1))
ggplot(data = sfmsall5) +
  geom_tile(aes(x = ms, y = reorder(eid,-plotorder), fill = alphaFctr)) +
  #scale_fill_gradient(low = 'grey90', high = '#0868ac', name = "occurrence %") +
  scale_fill_brewer(palette = "Blues", name = "Occurrence %", labels = c("(0-1]%", "(1-5]%", "(5-10]%","(10-25]%", "(25-50]%", "(50-75]%", "(75-100]%")) +
  labs(x = "Microstep No.", y = "Edges (ordered by total # occurrences)") +
  ThemeNoNet +
  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank(), panel.grid = element_blank())
@

>>>>

ggplot(data = simu2) +
  geom_density(aes(x = estimate, fill = Model), alpha = .5) +
  facet_wrap(~parameter, scales = 'free') +
  ThemeNoNet +
  scale_fill_brewer(palette = "Greys") + 
  theme(legend.position = 'bottom')
@

@@

<<sigtesting, fig.show = 'hold', out.width='\\textwidth', fig.height=2, fig.cap="Significant effects for the two data sets, at a significance level of 0.10 or lower as calculated by the Wald-type test available in the SIENA software.", error=FALSE>>=
smfr_effs <- read_csv("data/effects_significance_smallFriends.csv")
smfr_effs$inter1[is.na(smfr_effs$inter1)] <- "none"
library(ggrepel)
set.seed(12345678)
smfr_effs %>% filter(type == "eval" & Waldpval <=0.10) %>%
ggplot(aes(x = estimate, y = Waldpval, shape = inter1)) +
  #geom_errorbarh(aes(xmin = estimate - se, xmax = estimate + se), color = 'black') +
  geom_vline(xintercept = 0) +
  geom_point(size = 3, alpha = .75) +
  #geom_text_repel(aes(label = shortName)) +
  scale_shape(name = "Interaction\nVariable") +
  ggtitle("Significant effects at level 0.10 for friendship data") +
  coord_flip() +
  ThemeNoNet
sen_effs <- read_csv("data/congress/senateModelSigEffects.csv")
#sen_effs$Waldpval <- parse_number(sen_effs$Waldpval)
sen_effs$inter1[is.na(sen_effs$inter1)] <- "none"
ggplot(data = sen_effs %>% filter(Waldpval <=0.10), aes(x = estimate, y = Waldpval, shape= inter1)) +
  # geom_errorbarh(aes(xmin = estimate - se, xmax = estimate + se), color = 'black') +
  geom_vline(xintercept = 0) +
  geom_point(size = 3) +
  #geom_text_repel(aes(label = shortName)) +
  scale_shape(name = "Interaction\nVariable") +
  ggtitle("Significant effects at level 0.10 for senate data") +
  coord_flip() +
  ThemeNoNet
@

@@

ggplot(data = combinedavgs) +
  geom_net(aes(from_id = from, to_id = to, linewidth= linewidth),
           directed = T, curvature = .2, labelon=T, size = 3,
           arrow = arrow(angle = 20, type = "open", length = unit(.2, "cm")), ecolour = "#969696", fiteach = T,
           color = "#252525", hjust = .5, vjust = .5, labelcolour = 'white', fontsize = 2, arrowgap = .02,
           singletons = T) +
  ThemeNet + theme(panel.background = element_rect(color = 'black')) +
  facet_wrap(~cat)
@

@@

%Outdegree and reciprocity have the same inverse relationship for both data sets. For the friendship data, the inclusion of $\\beta_3$ has strong effect on the estimates of the other two parameters, but not for the senate data.
<<compareModels, fig.cap="Density plots of objective function parameter estimates from repeatedly fitting models M1, M2, and M3 to the example data. ", fig.height = 3>>=
simu2$data <- "friends"
senateEsts$data <- "senate"
allDataEsts <- rbind(senateEsts, simu2)
allDataEsts$parameter <- as.factor(allDataEsts$parameter)
allDataEsts$parameter <- ordered(allDataEsts$parameter, levels = c(paste0("alpha", 1:3),paste0("beta", 1:4)))
ggplot(allDataEsts %>% filter(str_detect(parameter, "beta"))) +
  geom_density(aes(x = estimate, fill = Model), alpha = .5) +
  facet_grid(data~parameter, scales = "free", labeller = "label_both") +
  scale_fill_brewer(palette = "Greys") + 
  ThemeNoNet +
  theme(legend.position = 'bottom')
@

@@

simu2 <- read.csv("data/simulation-1000-M1-M2-M3.csv")
simu_spread <- simu2 %>% spread(parameter, estimate)
ggpairs(simu_spread, columns = 3:8, aes(colour=Model, alpha = .5)) + 
  theme(plot.title = element_text(size = 10,
                                            face = 'plain', angle = 0, family = "Times New Roman"),
                  axis.title.x = element_text(size = 10,
                                            face = 'plain', angle = 0, family = "Times New Roman", inherit.blank = T),
                  axis.title.y = element_text(size = 10,
                                            face = 'plain', angle = 90, inherit.blank = T),
                  axis.text.x= element_text(size = 10,
                                            face = 'plain', angle = 90, inherit.blank = TRUE),
                 # axis.text.x.bottom = element_text(size = 10,
             #                               face = 'plain', angle = 90, inherit.blank = TRUE),
                  axis.text.y = element_text(size = 10,
                                            face = 'plain', angle = 0, family = "Times New Roman", inherit.blank = T),
                #  axis.text.y.right = element_text(size = 12,
               #                             face = 'plain', angle = 0, family = "Times New Roman", inherit.blank = T),
                  strip.text.x = element_text(size = 12,
                                            face = 'plain', angle = 0, family = "Times New Roman",
                                            margin = margin(t = 3, r = 0, b = 3, l = 0, unit = "pt"), inherit.blank = T),
                  strip.text.y =element_text(size = 12,
                                            face = 'plain', family = "Times New Roman", angle = 90,margin = margin(t = 3, r = 3, b = 3, l = 3, unit = "pt"),inherit.blank = T),
                  strip.background = element_rect(colour = "black", fill = "white")
                    )
@

@@

sfmsall5 <- sfmsall4 %>% ungroup %>% add_row(ms = max(sfmsall4$ms) + 1,
        eid = wave2$eid,
        count = NA,
        alpha = 1,
        from = wave2$from,
        to = wave2$to,
        total = wave2$total,
        plotorder = wave2$plotorder)
sfmsall5$alphaFctr <- cut(sfmsall5$alpha, c(0,.01, .05, .10, .25, .5, .75, 1, 1.1))
ggplot(data = sfmsall5) +
  geom_tile(aes(x = ms, y = reorder(eid,-plotorder), fill = alphaFctr)) +
  #scale_fill_gradient(low = 'grey90', high = '#0868ac', name = "occurrence %") +
  scale_fill_brewer(palette = "Greys", name = "Occurrence %", labels = c("(0-1]%", "(1-5]%", "(5-10]%","(10-25]%", "(25-50]%", "(50-75]%", "(75-100]%")) +
  labs(x = "Microstep No.", y = "Edges (ordered by total # occurrences)") +
  ThemeNoNet +
  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank(), panel.grid = element_blank())
@
